Overview

### 2021-04-23 overview_gh.Rmd
Seededlda (#42)
Add support for seeded LDA. Ref #39 


Co-authored-by: msaeltzer <msaeltze@mail.uni-mannheim.de>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM` and Keyword Assisted Topic Models from `keyATM`.

>>>>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM` and seeded LDA models from `seededlda`.
